---
title: "PCA Analysis"
output:
  html_document:
    df_print: paged
---
```{r libraries, include = FALSE}
library(tidyverse)
library(FactoMineR) # to run PCA
library(factoextra) # to make PCA plot
library(corrplot) # build pca correlation plot
```

```{r import, include = FALSE}
pca <- read.table("data/pca_noise.txt", header = TRUE)
colnames(pca) <- c('Impervious','Road Distance','Traffic Distance', 'Traffic', 'Road Length', 'Traffic Impact', 'Category')
pca <- pca %>% 
  mutate(Category = fct_relevel(factor(Category), "Urban", "Rural"))
pca <- pca[, c(1, 3, 4, 5, 2, 6, 7)]
site.pca <- PCA(pca[,1:4], graph = FALSE)
```

```{r correlation_plot, echo = FALSE, message = FALSE, warning = FALSE}
fviz_eig(site.pca, addlabels = TRUE)
var <- get_pca_var(site.pca)
corrplot(var$cos2, is.corr=FALSE)
```

All variables contribute to Dimension 1. Traffic has a larger contribution to Dimension 2 than 1. Dimension 1 explains `r round(site.pca$eig[1,2], 1)`% of the variance, and Dimension 2 explains `r round(site.pca$eig[2,2], 1)`% of the variance. 

We defined urban as sites that had more urban than agricultural land cover within a 1 km radius. Sites with more agricultural land cover are designated as rural.

```{r land_cover, echo = FALSE, warning = FALSE, message = FALSE, results = 'hide'}
# sorted by pc1
land_cover <- read.csv("data/site_land_cover.csv", header = TRUE) %>% 
  mutate(Site = factor(Site),
         Site = fct_relevel(Site, "7A", "5A", "6B", "6C", "6A", "7B", "3B", "2C", "1A", "3C", "1B", "2A", "2B", "4C", "8A", "7C", "5B", "5C", "3A", "1C", "4A", "4B", "8B"),
         Land_Cover = factor(Land_Cover),
         Land_Cover = fct_relevel(Land_Cover, "Other", "Agriculture", "Urban"))

land <- land_cover %>% 
ggplot(aes(x = Site, y = Percent, fill = Land_Cover)) +
  geom_col(position = "fill") +
  ylab("Proportion of Land Cover Class in 1 km Radius") +
  scale_fill_manual("Land Cover", 
                        values = c("#666666", "#1B9E77", "#D95F02"), 
                        labels = c("Other", "Agriculture", "Urban")) +
  theme_classic() +
  theme(text = element_text(size = 9, color = "black", family = "sans"), 
        axis.title = element_text(size = 9, family = "sans"), 
        axis.text = element_text(size = 6, color = "black", family = "sans"),
        legend.position = "top")

jpeg("figures/land.jpeg", width = 3.25, height = 3.25, units = "in", quality = 100, res = 300)
print(land)
dev.off()

land
```

Now we can form a PCA plot with sites colored by category.

```{r pca_plot, echo = FALSE , message = FALSE, warning = FALSE, results = 'hide'}
pca_plot <- fviz_pca_biplot(site.pca,
                repel = TRUE,
                fill.ind = pca$Category,
                col.ind = pca$Category,
                palette = c("#D95F02", "#1B9E77"),
                labelsize = 3,
                pointsize = 2.0,
                pointshape = 21,
                axes.linetype = "dotted",
                mean.point = FALSE,
                col.var = "grey40",
                xlab = "Principal Component 1 (70.9%)",
                ylab = "Principal Component 2 (18.3%)",
                title = "",
                ggtheme = theme_classic() + 
                  theme(text = element_text(size = 10))) +
  xlim(-3.5, 3.5) +
  ylim(-1.5, 2.5) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(colour = "black", size = 10, family = "sans")) +
  theme(axis.text.y = element_text(colour = "black", size = 10, family = "sans")) +
  theme(axis.title.x = element_text(colour = "black", size = 10, family = "sans")) +
  theme(axis.title.y = element_text(colour = "black", size = 10, family = "sans")) 

jpeg("figures/pca.jpeg", width = 4, height = 4, units = "in", quality = 100, res = 300)
print(pca_plot)
dev.off()

pca_plot

pca_plot2 <- fviz_pca_biplot(site.pca,
                repel = TRUE,
                label ="ind",
                fill.ind = pca$Category,
                col.ind = pca$Category,
                palette = c("#D95F02", "#1B9E77"),
                labelsize = 3,
                pointsize = 2.0,
                pointshape = 21,
                axes.linetype = "dotted",
                mean.point = FALSE,
                col.var = "grey40",
                xlab = "Principal Component 1 (70.9%)",
                ylab = "Principal Component 2 (18.3%)",
                title = "",
                ggtheme = theme_classic() + 
                  theme(text = element_text(size = 10))) +
  xlim(-3.5, 3.5) +
  ylim(-1.5, 2.5) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(colour = "black", size = 10)) +
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(axis.title.x = element_text(colour = "black", size = 10)) +
  theme(axis.title.y = element_text(colour = "black", size = 10)) 

jpeg("figures/pca2.jpeg", width = 4, height = 4, units = "in", quality = 100, res = 300)
print(pca_plot2)
dev.off()

pca_plot2
```

Urban and rural sites split well along the first dimension, but not the second. We will use dimension one in further analyses. 

Let's get dimension 1 values and save it as pca_results. 

```{r get_dimensions, echo = FALSE, message = FALSE, warning = FALSE}
dims <- data.frame(site.pca$ind$coord)
pca_fixed <- pca 
pca_fixed$site <- rownames(pca)
rownames(pca_fixed) <- NULL
dims$site <- rownames(dims)
rownames(dims) <- NULL
pca_results <- full_join(pca_fixed, dims, by = "site")
#saveRDS(pca_results, file = "data/pca_results.rds")
pca_results
```
