---
title: "PCA Analysis"
output:
  html_document:
    df_print: paged
---
```{r libraries, include = FALSE}
library(tidyverse)
library(FactoMineR) # to run PCA
library(factoextra) # to make PCA plot
library(corrplot) # build pca correlation plot
```

```{r import, include = FALSE}
pca <- read.table("data/pca_noise.txt", header = TRUE)
colnames(pca) <- c('Impervious','Road Distance','Traffic Distance', 'Traffic', 'Road Length', 'Traffic Impact', 'Category')
pca <- pca %>% 
  mutate(Category = fct_relevel(factor(Category), "Urban", "Rural"))
pca <- pca[, c(1, 3, 4, 5, 2, 6, 7)]
site.pca <- PCA(pca[,1:4], graph = FALSE)
```

```{r correlation_plot, echo = FALSE, message = FALSE, warning = FALSE}
fviz_eig(site.pca, addlabels = TRUE)
var <- get_pca_var(site.pca)
corrplot(var$cos2, is.corr=FALSE)
```

All variables contribute to Dimension 1. Traffic impact has a larger contribution to Dimension 2 than 1. Dimension 1 explains 74.7% of the variance, and Dimension 2 explains 20.6% of the variance. 

```{r pca_plot, echo = FALSE , message = FALSE, warning = FALSE}
pca_plot <- fviz_pca_biplot(site.pca,
                repel = TRUE,
                fill.ind = pca$Category,
                col.ind = pca$Category,
                palette = c("#D95F02", "#1B9E77"),
                labelsize = 3,
                pointsize = 2.0,
                pointshape = 21,
                axes.linetype = "dotted",
                mean.point = FALSE,
                col.var = "grey40",
                xlab = "Principal Component 1 (70.9%)",
                ylab = "Principal Component 2(18.3%)",
                title = "",
                ggtheme = theme_classic() + 
                  theme(text = element_text(size = 10))) +
  xlim(-3.5, 3.5) +
  ylim(-1.5, 2.5) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(colour = "black", size = 10)) +
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(axis.title.x = element_text(colour = "black", size = 10)) +
  theme(axis.title.y = element_text(colour = "black", size = 10)) 

jpeg("figures/pca.jpeg", width = 4, height = 4, units = "in", quality = 100, res = 300)
print(pca_plot)
dev.off()

pca_plot

pca_plot2 <- fviz_pca_biplot(site.pca,
                repel = TRUE,
                label ="ind",
                fill.ind = pca$Category,
                col.ind = pca$Category,
                palette = c("#D95F02", "#1B9E77"),
                labelsize = 3,
                pointsize = 2.0,
                pointshape = 21,
                axes.linetype = "dotted",
                mean.point = FALSE,
                col.var = "grey40",
                xlab = "Principal Component 1 (70.9%)",
                ylab = "Principal Component 2(18.3%)",
                title = "",
                ggtheme = theme_classic() + 
                  theme(text = element_text(size = 10))) +
  xlim(-3.5, 3.5) +
  ylim(-1.5, 2.5) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(colour = "black", size = 10)) +
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(axis.title.x = element_text(colour = "black", size = 10)) +
  theme(axis.title.y = element_text(colour = "black", size = 10)) 

jpeg("figures/pca2.jpeg", width = 4, height = 4, units = "in", quality = 100, res = 300)
print(pca_plot2)
dev.off()

pca_plot2
```

We defined urban as sites that had more urban than agricultural land cover within a 1 km radius. Sites with more agricultural land cover are designated as rural. Urban and rural sites split well along the first dimension, but not the second. We will use dimension one in further analyses. 

Let's get dimension 1 values and save it as pca_results. 

```{r get_dimensions, echo = FALSE, message = FALSE, warning = FALSE}
dims <- data.frame(site.pca$ind$coord)
pca_fixed <- pca 
pca_fixed$site <- rownames(pca)
rownames(pca_fixed) <- NULL
dims$site <- rownames(dims)
rownames(dims) <- NULL
pca_results <- full_join(pca_fixed, dims, by = "site")
#saveRDS(pca_results, file = "data/pca_results.rds")
pca_results
```
